Report on the Third Workshop on Sustainable Software for Science: Practice and Experiences (WSSSPE3)

### 2015-10-25 WSSSPE3/report/wg_appendix_software_credit.tex
added missing ref for Mozilla Contributorship Badges

Initial discussions focused on both various mechanisms for, and the philosophical approach behind, crediting software in scientific papers.
These began with proposals for various ways to credit software (or other research products including data) that contributed more significantly than a generic citation, including
\begin{itemize}
    \item A hierarchy of citations, with a ``substantial'' citation category to indicate software or data that played a more significant role in the research;
    \item Transitive credit~\cite{wssspe2_katz,Katz:2014_tc}, which assigns contriponents (contributors and components) various weights depending on their level of importance; and
    \item Project CRediT~\cite{projectcredit}, which assigns roles to paper authors based on their specific contributions; and
    \item Mozilla Science Lab's recently introduced Contributorship Badges for Science, which provide a badge---associated with ORCID~\cite{orcid}---based on author contributions in a similar manner to Project CRediT.
\end{itemize}
However, as of this writing, only the Project CRediT roles~\cite{McCall2015_credit,Lin2015_credit} and Contributorship Badges~\cite{} have been implemented in published papers, though both of these only provide a single ``Software'' or ``Computation'' category associated with software.
In addition, neither of these options allow for the citation of software itself, but only provide an author contribution related to software.
The discussion quickly focused on transtitive credit as a more quantitative measure of allocating credit to both authors and software, although there were some concerns about authors overestimating their own contributions compared to prior work.

>>>>

Initial discussions focused on both various mechanisms for, and the philosophical approach behind, crediting software in scientific papers.
These began with proposals for various ways to credit software (or other research products including data) that contributed more significantly than a generic citation, including
\begin{itemize}
    \item A hierarchy of citations, with a ``substantial'' citation category to indicate software or data that played a more significant role in the research;
    \item Transitive credit~\cite{wssspe2_katz,Katz:2014_tc}, which assigns contriponents (contributors and components) various weights depending on their level of importance; and
    \item Project CRediT~\cite{projectcredit}, which assigns roles to paper authors based on their specific contributions; and
    \item Mozilla Science Lab's recently introduced Contributorship Badges for Science~\cite{Mozilla_badges}, which provide a badge---associated with ORCID~\cite{orcid}---based on author contributions in a similar manner to Project CRediT.
\end{itemize}
However, as of this writing, only the Project CRediT roles~\cite{McCall2015_credit,Lin2015_credit} and Contributorship Badges~\cite{Mozilla_badges} have been implemented in published papers, though both of these only provide a single ``Software'' or ``Computation'' category associated with software.
In addition, neither of these options allow for the citation of software itself, but only provide an author contribution related to software.
The discussion quickly focused on transtitive credit as a more quantitative measure of allocating credit to both authors and software, although there were some concerns about authors overestimating their own contributions compared to prior work.
